Signal Processing to Demodulate FM Radio

### 2020-12-16 doc/paper/paper.tex
demod mono, stereo

\section{Demodulation of Broadcast FM}
  % mono:   just LP on 15 kHz
  % stereo: sum (L+R) + (L-R) = 2 L, (L+R) - (L-R) = 2R

@@

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Matlab Simulation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Demodulation of Broadcast FM}
  This chapter is describing the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
  The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec_fm_sig_demod} is already done correctly.
  A frequency spectrum of an FM channel is shown in Fig.\ref{fig_channel_baseband_freqs} above.

  \subsection{Mono}
    The first part of the channel frequency spectrum is the summation signal of the left and right audio channel.
    A mono receiver can thus simply replay the so-called multiplex signal, which is generated by the FM demodulation described in chapter \ref{sec_fm_sig_demod}. The 19 kHz pilot tone will not be audible by most people, because it is outside of the range of a human ear. Besides that, any used speaker may also be unable to produce a frequency in this range. This explanation applies to several higher frequency components in the spectrum as well.
    In order to be able to decimate the signal to a lower samplerate, for example to store it in a file with 44.1 kHz samplerate, a lowpass needs to be inserted before the decimation and output.
    The lowpass' cutoff frequency needs to be configured after 15 kHz.
    The filter needs to reach a sufficient attenuation before the pilot tone at 19 kHz.

  \subsection{Stereo}
    Demodulating an FM channel to recover a stereo audio signal, requires a more sophisticated approach.
    In the channel frequency spectrum, there are two main parts of the audio signal, the left-right sum and -difference signals.
    To combine these to a stereo signal, the following equations can be applied.
    \begin{equation*}
      L = (L+R) + (L-R) = (2)L
    \end{equation*}
    \begin{equation*}
      R = (L+R) - (L-R) = (2)R
    \end{equation*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Matlab Simulation}
  % TODO: insert entire block diagram of demodulation
  %       HF => abs() => discriminator => AM demod => audio
